Relational Parametricity for Algebraically Indexed Types

### 2012-05-17 paper/paper.tex
Fill in definition of \relSum

%FIXME: re-word this
A given relation context $\rho \in \relEnv{E}(\Delta)$ is extended to
a relation interpretation of any type $\Delta \vdash A : \sortType$ by
induction its derivation. So we define a relation
$\rsem{A}{\relEnv{E}}{\rho} \in \Rel(\tySem{A})$ for each well-formed
type $A$.
\begin{eqnarray*}
  \rsem{\tyUnit}{\relEnv{E}}\rho & = & \{(*,*)\} \\
  \rsem{\tyPrim{X}{e}}{\relEnv{E}}\rho & = & \rho_{\tyPrimNm{X}}(e) \\
  \rsem{A \tyArr B}{\relEnv{E}}\rho & = & \rsem{A}{\relEnv{E}}\rho \relArrow \rsem{B}{\relEnv{E}}\rho \\
  \rsem{A \tyProduct B}{\relEnv{E}}\rho & = & \rsem{A}{\relEnv{E}}\rho \relTimes \rsem{B}{\relEnv{E}}\rho \\
  \rsem{A + B}{\relEnv{E}}\rho & = & \rsem{A}{\relEnv{E}}\rho \relSum \rsem{B}{\relEnv{E}}\rho \\
  \rsem{\forall i\mathord:s.A}{\relEnv{E}}\rho & = & \bigcap\{ \rsem{A}{\relEnv{E}}\rho' \sepbar \rho' \in \extends{\rho}{i:s} \}
\end{eqnarray*}
In this definition we have made use of the following two constructions
on binary relations. If $R \in \Rel(X)$ and $S \in \Rel(Y)$, then $R
\relArrow S \in \Rel(X \to Y)$ is defined as $\{ (f_1,f_2) \sepbar
\forall (a_1,a_2) \in R.\ (f_1a_1,f_2a_2) \in S \}$. With the same
assumptions on $R$ and $S$, the relation $R \relTimes S \in \Rel(X
\times Y)$ is defined as $\{ ((a_1,b_1),(a_2,b_2)) \sepbar (a_1,a_2)
\in R \land (b_1,b_2) \in S \}$. FIXME: do $\relSum$.

>>>>

%FIXME: re-word this
A given relation context $\rho \in \relEnv{E}(\Delta)$ is extended to
a relation interpretation of any type $\Delta \vdash A : \sortType$ by
induction its derivation. So we define a relation
$\rsem{A}{\relEnv{E}}{\rho} \in \Rel(\tySem{A})$ for each well-formed
type $A$.
\begin{eqnarray*}
  \rsem{\tyUnit}{\relEnv{E}}\rho & = & \{(*,*)\} \\
  \rsem{\tyPrim{X}{e}}{\relEnv{E}}\rho & = & \rho_{\tyPrimNm{X}}(e) \\
  \rsem{A \tyArr B}{\relEnv{E}}\rho & = & \rsem{A}{\relEnv{E}}\rho \relArrow \rsem{B}{\relEnv{E}}\rho \\
  \rsem{A \tyProduct B}{\relEnv{E}}\rho & = & \rsem{A}{\relEnv{E}}\rho \relTimes \rsem{B}{\relEnv{E}}\rho \\
  \rsem{A + B}{\relEnv{E}}\rho & = & \rsem{A}{\relEnv{E}}\rho \relSum \rsem{B}{\relEnv{E}}\rho \\
  \rsem{\forall i\mathord:s.A}{\relEnv{E}}\rho & = & \bigcap\{ \rsem{A}{\relEnv{E}}\rho' \sepbar \rho' \in \extends{\rho}{i:s} \}
\end{eqnarray*}
In this definition we have made use of the following three
constructions on binary relations. If $R \in \Rel(X)$ and $S \in
\Rel(Y)$, then $R \relArrow S \in \Rel(X \to Y)$ is defined as $\{
(f_1,f_2) \sepbar \forall (a_1,a_2) \in R.\ (f_1a_1,f_2a_2) \in S
\}$. With the same assumptions on $R$ and $S$, the relation $R
\relTimes S \in \Rel(X \times Y)$ is defined as $\{
((a_1,b_1),(a_2,b_2)) \sepbar (a_1,a_2) \in R \land (b_1,b_2) \in S
\}$. Finally, the relation $R \relSum S \in \Rel(X + Y)$ is defined as
$\{ (\mathrm{inl}\ x, \mathrm{inl}\ x') \sepbar (x,x') \in R \} \cup
\{ (\mathrm{inr}\ y, \mathrm{inr}\ y') \sepbar (y,y') \in S \}$.
